Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-02 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Changing quotes to its own environment

%Please help with this paragraph, is evidence needed?
% It's the tuning of the algorithm which is data driven, not the
% algorithm itself, right? - JJ
%  Tuning yes - Mario
% And evidence for what? - jj
%  That most EAs use only population data - Mario
In evolutionary computation algorithms are data driven since it is important to keep data about the 
population of each generation, in order to generate the next or even change certain parameters
or analyze the evolutionary process. 
% Human Centered Importance
The framework models the context of interaction along with the population and
this knowledge is available to be an integral part of the evolutionary computation.
%This could be generalized?
For example, in a C-IEC application, fitness assignment depend on the
actions of a social network of users. 
A stream of actions is triggered when they tag, share, rate, store or even delete a phenotype. 
The selection of parents could also depend also on the previous actions, leveraging information 
such as the fact that they have the same tag, or are shared by
similar users. That knowledge could also be applied in choosing which phenotypes present to a certain
users, in order to give them those they will find more interesting or useful. 
% IoT
The context of interaction, can also include data retrieved from sensors and other IoT devices.
% Engagement
Data available from the interaction is also used to increase the performance of the system by applying 
gamification techniques. Gamification is defined by Deterding et al. as
``the use of game design elements in non-game contexts'' \cite{deterding2011game}.
The gamification element employed in a case study is a rewarding mechanism  
\cite{dubois2013understanding}, in general they consist of a reputation system with score points, 
levels and leader boards. Points are awarded to users in response of 
the accomplishment of certain activities that need to be encouraged. Levels depend
on the score and certain features of the game are only available to gamers when 
they reach a giving level.

@@

\begin{itemize}
\item {\bf Users are human} 
  The framework follows the approach of human centered computing \cite{sebe2010human},
  in which the context, environment, interfaces, preferences, accessibility, human relations, cognitive
  limitations, culture, creativity and other human aspects are an integral part of the system.
  Humans are the computing resorces of the system, having unique characteristics as those identified by 
  Sun \& Dance \cite{Sun2013}  ``(1) humans can solve computer hard problems; (2) humans are very good at exception handling, (3) humans have creativity, (4) humans have cognitive load limitation, (5) humans are vulnerable to 
  psychological manipulation, (6) humans are prone to errors, especially for reflective tasks.''

@@

\item {\bf Context of use matters}
  \textit{Context} In computer science Fischer \cite{fischer2012context}
  defines context as \textit{``the interaction between humans and
  computers in socio-technical systems that takes place in a certain
  context referring to the physical and social situation in which
  computational devices and environments are embedded''}. 
  Fischer also identifies the important aspects to consider when the context is used: how it is
  the contextual data obtained, how the context is represented and what
  goals and purposes the context has when is used in a particular
  application.   An IEC system will  be used within a certain range of technical, physical and social or
  organizational environments \cite{maguire2001context} that may affect its use.
  The concept has been formally defined
  by ISO standard 9241-11 \cite{international1998iso} as \textit{``users,
  tasks and equipment (hardware, software and materials), and the
  physical and social environments in which a product is used"}.

>>>>

%Please help with this paragraph, is evidence needed?
% It's the tuning of the algorithm which is data driven, not the
% algorithm itself, right? - JJ
%  Tuning yes - Mario
% And evidence for what? - jj
%  That most EAs use only population data - Mario
In evolutionary computation algorithms are data driven since it is important to keep data about the 
population of each generation, in order to generate the next or even change certain parameters
or analyze the evolutionary process. 
% Human Centered Importance
The framework models the context of interaction along with the population and
this knowledge is available to be an integral part of the evolutionary computation.
%This could be generalized?
For example, in a C-IEC application, fitness assignment depend on the
actions of a social network of users. 
A stream of actions is triggered when they tag, share, rate, store or even delete a phenotype. 
The selection of parents could also depend also on the previous actions, leveraging information 
such as the fact that they have the same tag, or are shared by
similar users. That knowledge could also be applied in choosing which phenotypes present to a certain
users, in order to give them those they will find more interesting or useful. 
% IoT
The context of interaction, can also include data retrieved from sensors and other IoT devices.
% Engagement
Data available from the interaction is also used to increase the performance of the system by applying 
gamification techniques. Gamification is defined by Deterding et al. \cite{deterding2011game} as
\begin{quote}
  the use of game design elements in non-game contexts.
\end{quote}  
The gamification element employed in this case study has been a rewarding mechanism  
\cite{dubois2013understanding}. In general rewards  consist of a reputation system with score points, 
levels and leader boards. Points are awarded to users in response of 
the accomplishment of certain activities that need to be encouraged. Levels depend
on the score and certain features of the game are only available to gamers when 
they reach a giving level. % Say what we are doing in this case - JJ

@@

\begin{itemize}
\item {\bf Users are human} 
  The framework follows the approach of human centered computing \cite{sebe2010human},
  in which the context, environment, interfaces, preferences, accessibility, human relations, cognitive
  limitations, culture, creativity and other human aspects are an integral part of the system.
  Humans are the computing resorces of the system, having unique characteristics as those identified by 
  Sun \& Dance \cite{Sun2013}
\begin{quote}
  (1) humans can solve computer hard problems; (2) humans are very good at exception handling, (3) humans have creativity, (4) humans have cognitive load limitation, (5) humans are vulnerable to 
  psychological manipulation, (6) humans are prone to errors,
  especially for reflective tasks.
\end{quote}

@@

\item {\bf Context of use matters}
  \textit{Context} In computer science Fischer \cite{fischer2012context}
  defines context as
  \begin{quote}
  the interaction between humans and
  computers in socio-technical systems that takes place in a certain
  context referring to the physical and social situation in which
  computational devices and environments are embedded.
\end{quote}   
  Fischer also identifies the important aspects to consider when the context is used: how it is
  the contextual data obtained, how the context is represented and what
  goals and purposes the context has when is used in a particular
  application.   An IEC system will  be used within a certain range of technical, physical and social or
  organizational environments \cite{maguire2001context} that may affect its use.
  The concept has been formally defined
  by ISO standard 9241-11 \cite{international1998iso} as\begin{quote}
  users,
  tasks and equipment (hardware, software and materials), and the
  physical and social environments in which a product is used.
\end{quote}
